---
title: "Lab 5"
author: "Jaxon Stuhr"
date: "10/25/2021"
output: 
  html_document: 
    theme: journal
    toc: yes
    code_folding: hide
---

```{r setup, include=TRUE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(effsize)
```

## Part 1: Confidence Intervals

Using the 't.test()' to calculate confidence intervals

### Example 1

Create single mock sample containing a number of values, then learn to use 't.test()' to return confidence intervals and learn about in-line code referencing.

```{r}
# Create mock sample (vector of vals)
otter_lengths = c(22, 34, 26, 28, 39)
# Find confidence interval from sample, t distribution
otter_ci = t.test(otter_lengths)
# Find standard dev
otter_sd = sd(otter_lengths)
```
Mean otter length is 29.8 inches $\pm$ 6.7 (mean $\pm$ sd, n = 5) with a 95% confidence interval of [21.5, 38.1]

#### Now using in-line referencing

Mean otter length is `r round(otter_ci$estimate, 1)` inches with a 95% confidence interval of [`r round(otter_ci$conf.int[1], 1)`, `r round(otter_ci$conf.int[2], 1)`] inches.

## Part 2: Two-sample t-tests

Make two mock samples and ask question: do we have sufficient evidence to reject null hypotheses that these samples were drawn from popus w same mean

```{r}
# make me mock samples
oak_trees = c(20, 19, 24, 28, 34, 12, 15, 25)
pine_trees = c(39, 26, 20, 30, 37, 22, 19, 18)

# two-sample t-test
trees_t = t.test(oak_trees, pine_trees)
```
If samples were drawn from popus w the same mean, there is a 28.7% chance of taking samples from those populations with means at least as different as these observed means. 

The mean heights of oak and pine trees were (x +- y) and (x +- y), and the difference was not significant (t(`r round(trees_t$parameter,1)`) = `r round(trees_t$statistic,1)`, p = `r round(trees_t$p.value,1)`)

## Part 3: t-test w cars data

```{r}
compact_suv = mpg %>% 
  filter(class %in% c("compact", "suv"))
```

Create a histogram of city gas mileage (cty) faceted by class starting from compact_suv

```{r}
ggplot(data = compact_suv, aes(x = cty)) + 
  geom_histogram(bins = 12) + 
  facet_wrap(~ class)
```

```{r}
car_stats = compact_suv %>% 
  group_by(class) %>% 
  summarize(
    mean_city = round(mean(cty), 2),
    sd_city = sd(cty),
    sample_size = n()
  )

car_stats
```
The t.test function wants vectors! Use `pull()` function to pull out vector from data frame.

```{r}
compact_sample = compact_suv %>% 
  filter(class == "compact") %>% 
  pull(cty)

suv_sample = compact_suv %>% 
  filter(class == "suv") %>% 
  pull(cty)
```

```{r}
t.test(compact_sample, suv_sample)
```

Reject the nULLL!!!!!!





